---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# moiraine

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

`moiraine` is a package for facilitating the construction of a reproducible analysis pipeline for multi-omics data integration. It provides functions to automate data import, pre-processing, transformation, and integration through several tools. It relies on the [targets](https://books.ropensci.org/targets/) package to generate reproducible workflows. `moiraine` currently supports multi-omics data integration through:

-   sPLS and DIABLO from the mixOmics package;

-   sO2PLS from the omicsPLS package;

-   MOFA and MEFISTO from the MOFA2 package.


## Installation

You can install the development version of moiraine from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("PlantandFoodResearch/moiraine")
```

## Example

To get started, create a new analysis pipeline in your working directory with:

```{r example}
#| eval: false

library(moiraine)

create_moiraine_pipeline()
```

Before using `moiraine`, we encourage you to get familiar with the `targets` package; the [manual](https://books.ropensci.org/targets/) is a great place to start.
